Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
reformulate sentence

Rather than teaching developers about domain science, or domain scientists about
software development practices, why don't we teach both communities to
collaborate more effectively? Can this be done without teaching each side a
little of the other to enable communication, with a response that it really is
not two binary communities, but a spectrum with useful roles in the middle.
Someone else asked if a developer can be effective without being part of the
domain community, with responses that this really depends on the specific
problem---translators and T-shaped people are important. Why aren't academic
communities taught how to evaluate cross-disciplinary work well?

>>>>

Rather than teaching developers about domain science, or domain scientists about
software development practices, why don't we teach both communities to
collaborate more effectively? Can this be done without teaching each side a
little of the other to enable communication, with a response that it really is
not two binary communities, but a spectrum with useful roles in the middle.
The question was raised if a developer can be effective without being part of the
domain community, with responses that this really depends on the specific
problem---translators and T-shaped people are important. Why aren't academic
communities taught how to evaluate cross-disciplinary work well?
